Illustrating imputation of missing data using the Titanic dataset

### 2024-05-09 text/pending/titanic-imputation.Rmd
Added pending folder

---
title: Illustrating splines using the Titanic dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Nonlinear regression
- R programming
output: html_document
---

@@

Here is a brief description of the diamond pricing dataset, taken from the [data dictionary][sim3] on my github site.

@@

```{r}
summary(ti0$Age)
count(ti0, pclass)
count(ti0, sex)
count(ti0, survived)
```

>>>>

---
title: Illustrating imputation of missing data using the Titanic dataset
source: "New"
author: Steve Simon
date: 2024-05-07
categories:
- Blog post
tags:
- Missing data
- R programming
output: html_document
---

@@

Here is a brief description of this dataset, taken from the [data dictionary][sim3] on my github site.

@@

```{r}
summary(ti0$age)
count(ti0, pclass)
count(ti0, sex)
count(ti0, survived)
```

Notice the large number of missing values for age.
